---
title: "Readme"
output:
  html_document:
    toc: true
    theme: united
---

## Introduction

This program is divided into 13 different steps, and it generates a tidy data set from the data downloaded from [Here](https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip).

For more information: [Human-Activity-Recognition-Using-Smartphones](http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones)

## 1. Getting the data

In this first five steps, we perform the downloading operation, unziping process and finally we read the train and test data

```{r eval = FALSE}
# Step1: Download the required dataset
url <- "https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip"
download.file(url, file.path(pwd, "RAW_Data.zip"))

# Step2: Unzip the data
unzip(file.path(pwd, "RAW_Data.zip"), overwrite = TRUE, exdir = ".")

# Step3: Update the working dir reference without changing it
pwd <- file.path(pwd, "UCI HAR Dataset")

# Step4: Read the three train files
Subject_Train <- read.table(file.path(pwd, "train", "subject_train.txt"))
X_Train <- read.table(file.path(pwd, "train", "X_train.txt"))
Y_Train <- read.table(file.path(pwd, "train", "y_train.txt"))

# Step5: Read the three test files
Subject_Test <- read.table(file.path(pwd, "test", "subject_test.txt"))
X_Test <- read.table(file.path(pwd, "test", "X_test.txt"))
Y_Test <- read.table(file.path(pwd, "test", "y_test.txt"))
```

## 2. Getting tidy

In the steps six and seven, we R/W the label from the activities adn the features

```{r eval = FALSE}
# Step6: Read the column names from features.txt and set the names to the columns in X
ColLabels <- read.table(file.path(pwd, "features.txt"), colClasses = c("integer", "character"))
ColLabels <- ColLabels[, 2]
colnames(X_Train) <- ColLabels
colnames(X_Test) <- ColLabels

# Step7: Read the activiy labels and replace the numbers for the descriptive text in Y
ActivityLabels <- read.table(file.path(pwd, "activity_labels.txt"), colClasses = c("integer", "character"))
Y_Train <- data.frame(sapply(Y_Train, function(x){ActivityLabels[x,2]}))
Y_Test <- data.frame(sapply(Y_Test, function(x){ActivityLabels[x,2]}))
```